D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-04 ootavacuous.tex
Add JMM Causality Test Case 10
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
Add and use a DisplayRunLitmus directive
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-1.litmus @@
\end{verbatim}
\caption{Causality Test Case 1}
\label{lst:Causality Test Case 1}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-2.litmus @@
\end{verbatim}
\caption{Causality Test Case 2}
\label{lst:Causality Test Case 2}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-3.litmus @@
\end{verbatim}
\caption{Causality Test Case 3}
\label{lst:Causality Test Case 3}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-4.litmus @@
\end{verbatim}
\caption{Causality Test Case 4}
\label{lst:Causality Test Case 4}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-5.litmus @@
\end{verbatim}
\caption{Causality Test Case 5}
\label{lst:Causality Test Case 5}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-6.litmus @@
\end{verbatim}
\caption{Causality Test Case 6}
\label{lst:Causality Test Case 6}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-7.litmus @@
\end{verbatim}
\caption{Causality Test Case 7}
\label{lst:Causality Test Case 7}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-8.litmus @@
\end{verbatim}
\caption{Causality Test Case 8}
\label{lst:Causality Test Case 8}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-9.litmus @@
\end{verbatim}
\caption{Causality Test Case 9}
\label{lst:Causality Test Case 9}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-9a.litmus @@
\end{verbatim}
\caption{Causality Test Case 9a}
\label{lst:Causality Test Case 9a}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-non-lb.litmus @@
\end{verbatim}
\caption{Non-LB Litmus Test}
\label{lst:Non-LB Litmus Test}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-two-source.litmus @@
\end{verbatim}
\caption{Multi-Cycle Litmus Test}
\label{lst:Multi-Cycle Litmus Test}
\end{listing}

>>>>

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-1.litmus @@
\caption{Causality Test Case 1}
\label{lst:Causality Test Case 1}
\end{listing}

@@

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-2.litmus @@
\caption{Causality Test Case 2}
\label{lst:Causality Test Case 2}
\end{listing}

@@

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-3.litmus @@
\caption{Causality Test Case 3}
\label{lst:Causality Test Case 3}
\end{listing}

@@

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-4.litmus @@
\caption{Causality Test Case 4}
\label{lst:Causality Test Case 4}
\end{listing}

@@

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-5.litmus @@
\caption{Causality Test Case 5}
\label{lst:Causality Test Case 5}
\end{listing}

@@

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-6.litmus @@
\caption{Causality Test Case 6}
\label{lst:Causality Test Case 6}
\end{listing}

@@

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-7.litmus @@
\caption{Causality Test Case 7}
\label{lst:Causality Test Case 7}
\end{listing}

@@

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-8.litmus @@
\caption{Causality Test Case 8}
\label{lst:Causality Test Case 8}
\end{listing}

@@

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-9.litmus @@
\caption{Causality Test Case 9}
\label{lst:Causality Test Case 9}
\end{listing}

@@

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-9a.litmus @@
\caption{Causality Test Case 9a}
\label{lst:Causality Test Case 9a}
\end{listing}

\subsubsection{Causality Test Case 10}
\label{app:Causality Test Case 10}

Listing~\ref{lst:Causality Test Case 10}
shows causality test case 10, for which the \co{r1 == r2 == 1 && r3 == 0}
result is to be forbidden.
The herd7 tool nevertheless reports this result and does not flag it as
an OOTA cycle.

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-causality-10.litmus @@
\caption{Causality Test Case 10}
\label{lst:Causality Test Case 10}
\end{listing}

@@

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-non-lb.litmus @@
\caption{Non-LB Litmus Test}
\label{lst:Non-LB Litmus Test}
\end{listing}

@@

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-two-source.litmus @@
\caption{Multi-Cycle Litmus Test}
\label{lst:Multi-Cycle Litmus Test}
\end{listing}
